Compiling refinement types to dependent types

### 2020-07-25 tex/paper.tex
Fix the stuff in T-Abs translation
I was tired and probalby should've gone to sleep.

  \item \textsc{T-Abs}.
    \begin{align*}
      & \inferrule{\nonterm G \vdash (\gterm x : \nonterm{ts}_1) \rightarrow \nonterm{ts}_2 \\\\
                   \nonterm G , \gterm x : \nonterm{ts}_1 \vdash \nonterm{es} : \nonterm{ts}_2}
                  {\nonterm G \vdash \lambda x : \nonterm{ts}_1. \nonterm{es} : (\gterm x : \nonterm{ts}_1) \rightarrow \nonterm{ts}_2}
          \longmapsto
        \inferrule{\Tranty(\nonterm G \vdash (\gterm x : \nonterm{ts}_1) \rightarrow \nonterm{ts}_2) \\\\
                   \Tranterm(\nonterm G , \gterm x : \nonterm{ts}_1 \vdash \nonterm{es} : \nonterm{ts}_2)
                   }
                  {\nonterm G \vdash \lambda x : \nonterm{tc}_1. \nonterm{es} : \Pi \gterm x : \nonterm{tc}_1. \nonterm{tc}_2},    \\
      \text{where}~&\nonterm{GC} = \Tranctx(\nonterm G \ctxok),       \\
                   &\nonterm{tc}_1 = \tranty(\Gamma \vdash \nonterm{tc}_1), \\
                   &\nonterm{tc}_2 = \tranty(\Gamma , x : \nonterm{tc}_1 \vdash \nonterm{tc}_2), \\
                   &\nonterm{ec} = \tranterm().
    \end{align*}

>>>>

  \item \textsc{T-Abs}.
    \begin{align*}
      & \inferrule{\nonterm G \vdash (\gterm x : \nonterm{ts}_1) \rightarrow \nonterm{ts}_2 \\\\
                   \nonterm G , \gterm x : \nonterm{ts}_1 \vdash \nonterm{es} : \nonterm{ts}_2}
                  {\nonterm G \vdash \lambda x : \nonterm{ts}_1. \nonterm{es} : (\gterm x : \nonterm{ts}_1) \rightarrow \nonterm{ts}_2}
          \longmapsto
        \inferrule{\Tranty(\nonterm G \vdash (\gterm x : \nonterm{ts}_1) \rightarrow \nonterm{ts}_2) \\\\
                   \Tranterm(\nonterm G , \gterm x : \nonterm{ts}_1 \vdash \nonterm{es} : \nonterm{ts}_2)
                   }
                  {\nonterm{GC} \vdash \lambda x : \nonterm{tc}_1. \nonterm{ec} : \Pi \gterm x : \nonterm{tc}_1. \nonterm{tc}_2},    \\
      \text{where}~&\nonterm{GC} = \Tranctx(\nonterm G \ctxok),       \\
                   &\nonterm{tc}_1 = \tranty(\Gamma \vdash \nonterm{ts}_1), \\
                   &\nonterm{tc}_2 = \tranty(\Gamma , x : \nonterm{ts}_1 \vdash \nonterm{ts}_2), \\
                   &\nonterm{ec} = \tranterm(\nonterm G , \gterm x : \nonterm{ts}_1 \vdash \nonterm{es} : \nonterm{ts}_2).
    \end{align*}
